---
title: "Final Project"
author: "410411325 林皓翔，410511303 陳曼琳，410511331 李阜舫"
date: "2018年6月29日"
output: 
  html_document: 
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
      smooth_scroll: false
---
##1. Categorical Data: Ch09 (IPS6e) Exercises:(42-43: GOF to normal data) and Ch15 (STBE17e): Exercise 62 (data given in week 12)

```{r}
twins <- read.table("twins.dat.txt", header=T, sep=",", na.strings=".")
```


###3.4 (Categorizing ages in the twins dataset). The variable AGE gives the age (in years) of twin 1.
####a. Use the cut function on AGE with the breakpoints 30, 40, and 50 to create a categorized version of the twin’s age.
```{r}
obser. <- 1:183
age <- twins$AGE
twins.age <- data.frame(obser., age)
twins.age$age_category <- cut(age, breaks=c(0, 30, 40, 50, Inf), labels=c("age < 30", "30 < age < 40", "40 < age < 50", "50 < age"))
head(twins.age)
tail(twins.age)
```

####b. Use the table function to find the frequencies in the four age categories.
```{r}
table(twins.age$age_category)
```

####c. Construct a graph of the proportions in the four age categories.
```{r}
prop.ages <- table(twins.age$age_category)/length(twins.age$age_category)
barplot(prop.ages, ylim=c(0, 0.4))
box(bty="o")
```

###3.5 (Relating age and wage in the twins dataset). The variables AGE and HRWAGEL contain the age (in years) and hourly wage (in dollars) of twin 1.
####a. Using two applications of the cut function, create a categorized version of AGE using the breakpoints 30, 40, and 50, and a categorized version of HRWAGEL using the same breakpoints as in Section 3.3.
```{r}
obser. <- 1:183

age <- twins$AGE
twins.age <- data.frame(obser., age)
twins.age$age_category <- cut(age, breaks=c(0, 30, 40, 50, Inf), labels=c("age < 30", "30 < age < 40", "40 < age < 50", "50 < age"))
head(twins.age)

wage <- twins$HRWAGEH
twins.wage <- data.frame(obser., wage)
twins.wage$wage_category <- cut(wage, breaks=c(0, 7, 13, 20, 150), labels=c("wage < 7", "7 < wage < 13", "13 < wage < 20", "20 < wage < 150"))
head(twins.wage)
```

####b. Using the categorized versions of AGE and HRWAGEL, construct a contingency table of the two variables using the function table.
```{r}
(age_wage <- table(twins.age$age_category, twins.wage$wage_category))
```

####c. Use the prop.table function to find the proportions of twins in each age class that have the different wage groups.
```{r}
(prob <- prop.table(age_wage, margin=1))
```

####d. Construct a suitable graph to show how the wage distribution depends on the age of the twin.
```{r}
c.wage <- twins.wage$wage_category
barplot(t(prob), ylab="proportion", ylim=c(0, 1.2), legend.text=dimnames(prob)$c.age)
```

####e. Use the conditional proportions in part (c) and the graph in part (d) to explain the relationship between age and wage of the twins.

>觀察：<p>
(c)表格：年紀小於40歲的人，時薪大多小於13美元；年紀大於40歲的人，時薪大於13美元的比例較多。<p>
(d)圖：年紀小於30歲的人，時薪分布在小於7美元這個範圍的比例是最多的；反之，年紀大於50歲的人，雖然無法明顯看出與其他薪資分布比例差異，但跟其他歲數區間相比，時間大於20美元的比例的確比較高。<p>
><p>
>結論：<p>
隨著年紀增長，所賺取的時薪也會越來越多。<p>

###3.6 (Relating age and wage in the twins dataset, continued).
###a. Using the contingency table of the categorized version of AGE and HRWAGEL and the function chisq.test, perform a test of independence of age and wage. Based on this test, is there significant evidence to conclude that age and wage are dependent?

>Assume that H: Age and wage are independent.

```{r}
(S <- chisq.test(age_wage))
```

>Now, check the value of X-squared.
```{r}
sum((age_wage-S$expected)^2/S$expected)
```
>The answer is 17.99303, which agrees with the displayed value of X-squared from the chisq.test output.<p>
>
>Then, check the computation of the p-value.
```{r}
1-pchisq(17.993, df=9) 
```
>This also agrees with the p-value given in the chisq.test output. This p-value is very small, so the hypothesis of independence of age and wage is rejected. So age and wage are dependent. 
###b. Compute and display the Pearson residuals from the test of independence. Find the residuals that exceed 2 in absolute value.

```{r}
S$residuals
abs(S$residuals)>=2
```

####c. Use the function mosaicplot with the argument shade=TRUE to construct a mosaic plot of the table counts showing the extreme residuals.
```{r}
mosaicplot(age_wage, shade=T, main="Age & Wage")
```

####d. Use the numerical and graphical work from parts (b) and (c) to explain how the table of age and wages differs from an independence structure.

>觀察:<p>
>(b)表格：只有年紀小於30歲、時薪小於7美元的人的殘差絕對值小於2。<p>
>(c)圖：明顯地，所有區塊裡只有年紀小於30歲、時薪小於7美元的人被著色，而其顏色代表的是符合此條件的residual落在[2,4]。<p>
><p>
>結論：<p>
>根據定義，任何絕對值大於2的residual的含意是偏離獨立的情況是顯著的，所以可以推論一個不到30歲的人，時薪極有可能小於７美元。


##2. Basic Inference: Ch06 (Text) Exercises: (4, 5)
###6.4 An experiment was performed in an introductory statistics class to illustrate the concept of measurement bias. The instructor held up a string in front of the class and each student guessed at the string’s length. The following are the measurements from the 24 students (in inches).
###22 18 27 23 24 15 26 22 24 25 24 18
###18 26 20 24 27 16 30 22 17 18 22 26

####a. Use the scan function to enter these measurements into R.
```{r}
measurements = scan(text = "22 18 27 23 24 15 26 22 24 25 24 18 18 26 20 24 27 16 30 22 17 18 22 26")
```

####b. The true length of the string was 26 inches. Assuming that this sample of measurements represents a random sample from a population of student measurements, use the t.test function to test the hypothesis that the mean measurement μ is different from 26 inches.
$H_{0}$:$\mu$=26 <p>
$H_{a}$:$\mu$$\neq$ 26
```{r}
t.test(measurements, alternative = c("two.sided"), mu=26)
```

>因為P-value小於0.05，拒絕虛無假說，所以我們有信心說不等於26。

####c. Use the t.test function to find a 90% confidence interval for the population mean μ.
>為了找出90%的信賴區間，所以我們將信心水準訂為90%。
```{r}
t.test(measurements, conf.level = 0.90)
```

>我們利用t.test作出90%的信賴區，且信賴區間為[20.8573, 23.6427]，

####d. The t-test procedure assumes the sample is from a population that is normally distributed. Construct a normal probability plot of the measurements and decide if the assumption of normality is reasonable.
```{r}
qqnorm(measurements, main = "measurements", ylab = "length")
qqline(measurements, col="red")
```

>我們利用normal quantile-quantile plot，我們可看出母體是近似常態分配，滿足我們的假設。

###6.5 The datafile “buffalo.cleveland.snowfall.txt” contains the total snowfall in inches for the cities Buffalo and Cleveland for the seasons 1968-69 through 2008-09.

####a. Compute the differences between the Buffalo snowfall and the Cleveland snowfall for all seasons.
```{r}
snowfall = read.table("buffalo.cleveland.snowfall.txt", header=TRUE)
snowfalls=snowfall[,-1]
boxplot(snowfalls, horizontal=TRUE,xlab="snowfall")
```

>利用boxplot可以看出Buffalo的降雪量明顯比Cleveland多，不論平均數或是四分位距都是在Cleveland的右邊。

####b. Using the t.test function with the difference data, test the hypothesis that Buffalo and Cleveland get, on average, the same total snowfall in a season.
```{r}
Cleveland=snowfall$Cleveland
Buffalo=snowfall$Buffalo
(A=t.test(Buffalo,Cleveland,paired=TRUE))
```

>再來我們用統計方法去驗證兩邊的降雪量平均是否不同，利用Welch Two  Sample t-test 去檢驗，$H_{0}$:$\mu_{1}$=$\mu_{2}$    $H_{a}$:$\mu_{1}$$\neq$$\mu_{2}$，p-value非常的小遠小於0.05，所以我們拒絕這個虛無假說，因此我們有信心說兩個樣本數的平均數不相同。

####c. Use the t.test function to construct a 95% confidence interval of the mean difference in seasonal snowfall.
```{r}
cat("95% confidence interval of Buffalo and Cleveland=",A$conf.int)
```

<p>　　</p>
<p>　　</p>
##3. One-Way ANOVA: Ch08 (Text) Exercises: (3-4: Iris data)
###8.3 (Differences in iris by species). The iris data has 50 observations of four measurements for each of three species of iris: setosa, versicolor, and virginica. We are interested in possible differences in the sepal length of iris among the three species. Perform a preliminary analysis as in Example 8.3. Write the effects model for a one-way ANOVA. What are the unknown parameters? Next fit a one-way ANOVA model for Sepal.Length by Species using lm. Display the ANOVA table. What are the parameter estimates?

>我們感興趣的是鳶尾花(iris)的三種品種(setosa,versicolor,and virginica)間萼片長度是否存在差異性，
在統計上我們會從setosa，versicolor，virginica三個母體中進行抽樣並測量其萼片的長度作為我們的Sample data，再用這些數據進行統計推論，推測這些母體的平均值是否相同。
我們先假設這三個母體是服從互相獨立且有平均值$\mu_{1},\mu_{2},\mu_{3}$和共同的變異數$\sigma^{2}$的常態分配，而在這樣的假設下，我們感興趣的問題即是一個單因子變異數分析(ANOVA)的問題。
<p>　　虛無假說 $H_{0}$：$\mu_{1}=\mu_{2}=\mu_{3}$</p>
<p>　　對立假說 $H_{1}$：至少有兩個平均值不相等</p>
<p>One-way ANOVA model為：(means model)</p>
<p>　　　　　　　　$Y_{ij}=\mu_{i}+\epsilon_{ij}$,　　$i=1,2,3$,　$j=1,...,50$</p>
<p>另一種One-way ANOVA model形式為：(effects model)</p>
<p>　　　　　　　　$Y_{ij}=\mu+\tau_{i}+\epsilon_{ij}$,　　$i=1,2,3$,　$j=1,...,50$</p>
<p>　　隨機變數$Y_{ij}$是代表從第$i$個樣本抽出的第$j$個觀察值。</p>
<p>　　$\tau_{i}$是與母體$i$相關的一個參數，稱為第$i$個處理的效應(treatment effect)，</p>
<p>　　參數 $\mu$ 與 $\tau_{i}$ 滿足等式 $E\left[Y_{ij}\right]=\mu+\tau_{i}$，</p>
<p>　　在一些書中 $\mu$ 為grand mean(所有$\mu_{i}$的總平均)，即 $\mu=\frac{1}{3}\sum_{i=1}^{3}\mu_{i}$，</p>
<p>　　但在R語言中進行變異數分析時似乎並不是把grand mean作為 $\mu$。
<p>　　$\epsilon_{ij}$為隨機誤差，代表第$i$個樣本的第$j$個觀察值與對應處理平均之間的偏差。</p>
<p>　　</p>
<p>在此模型下可將虛無假說與對立假說轉換為</p>
<p>　　$H_{0}$：$\tau_{1}=\tau_{2}=\tau_{3}=0$</p>
<p>　　$H_{1}$：至少有一個$\tau_{i}$不等於$0$</p>
<p>　　</p>
<p>Unknown parameters are $\mu,\tau_{1},\tau_{2},\tau_{3},\sigma^{2}$</p>
<p>但在R by Example的課本中有提到，這樣未知的參數就比使用means model時多了一個，所以必須對其加些限制，將這5個參數轉換為其中4個參數的關係式。而在R中是讓$\tau_{1}=0$，即讓$\mu=\mu_{1}$，有點以treatment 1為基準，再衡量$\tau_{2},\tau_{3}$，另外兩品種與品種1組間變異的味道。</p>
<p>所以未知的參數變成：$\mu,\tau_{2},\tau_{3},\sigma^{2}$</p>
<p>　　</p>
<p>　　</p>
現在，我們開始使用R統計軟體進行變異數分析，R預裝的datasets包裡就已經有了可以作為Sample data使用的iris資料集

```{r}
str(iris)
head(iris)
table(iris$Species)
```

>該資料集有4個數值型變數，分別是Sepal.Length(萼片長)、Sepal.Width(萼片寬)、Petal.Length(花瓣長)、Petal.Width(花瓣寬)，1個類別型變數Species(品種)[one factor/3 levels: setosa, versicolor, and
virginica]，每個變數都有150筆觀測值，其中每種品種各有50筆。
<p>　　</p>
<p>我們先用`lm()`函數去配適萼片長度基於基於其品種的模型，並把結果存放至變數L中，</p>
<p>`lm(num ~ num)`當左右皆為數值型向量時，`lm`函數會配適一個線性回歸模型，</p>
<p>`lm(num ~ factor)`而當右邊放的是因素向量時，就能配適我們現在需要的ANOVA模型，</p>
<p>再對`lm`產生的物件L使用`anova()`函數即可秀出ANOVA Table。</p>

```{r}
L = lm(iris$Sepal.Length~iris$Species)
anova(L)
```

>p-value小於0.05，拒絕虛無假說，我們有信心說三個品種的平均數並不相同。

```{r}
L$coefficients
```

>這三個係數分別是使用最小平方法所估出來的參數 $\mu,\tau_{2},\tau_{3}$
<p>而Residuals的MSE *0.265* 則是$\sigma^{2}$的估計值</p>

```{r}
(Means = tapply(iris$Sepal.Length,iris$Species,mean))
```
>計算出三個樣本的平均數後可以確認到參數 $\mu$ 確實是treatment 1的mean $\mu_{1}$


###8.4 (Checking model assumptions). Refer to your results from Exercise 8.3. What are the assumptions required for inference? Analyze the residuals of the model to assess whether there is a serious departure from any of these assumptions. How can you check for normality of the error variable?

>為了進行推論所需要的假設為3個母體是具有相同變異數的常態分配，我們現在藉著分析配適後的殘差(residuals)來檢查我們的母體是否真的有貼近這些假設。


```{r, fig.width=9, fig.heigth=4}
par(mfrow=c(1,2))
plot(L$fit, L$res, main="Residuals vs Fitted", xlab="Fitted Values", ylab="Residuals")
abline(h=0, col="blue")

qqnorm(L$res, ylab="Sample Quantiles of Residuals")
qqline(L$res, col="blue")
```

><p>先畫出Fitted Values與Residuals的點散圖，這邊的Fitted Values即為使用最小平方法所預測出來的平均數，即$\widehat{\mu_{1}},\widehat{\mu_{2}},\widehat{\mu_{3}}$，y座標則為Sample data與其對應的母體平均數估測值之間的殘差，從圖中可看出這三組樣本的離散程度是有所差異的，與我們假設的具有相同變異數有些不符合，不過差異的程度並不是很嚴重，對分析結果的影響大概還在可接受的範圍。
<p>再來檢查殘差是否符合常態性，也就是模型裡面的error項是否滿足為常態分配的假設，我們可以藉由normal quantile-quantile plot來看其與標準常態分配理論值的百分位數是否有差不多的分配。從圖中和qqline可看出確實符合常態性的假設。</p>
